---
title: "1d_sim"
author: "Harrison Li"
date: "`r Sys.Date()`"
output: pdf_document
---

\newcommand{\aipsw}{\textnormal{aipsw}}
\newcommand{\or}{\textnormal{or}}
\newcommand{\collab}{\textnormal{collab}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(caret)
library(gam)
library(SuperLearner) 
library(grf)
library(tidyverse)
library(ggpattern)
PATH <- "/Users/harrisonli/Documents/GitHub.nosync/calibrating_large_scale_observations/"
source(paste0(PATH, "helpers.R"))
```

# Specify DGP

```{r}
# Specify Delta(x), based on Kallus et al. (2018)
Delta_fun <- function(x) {
  return(0.75*x^2 + 3*x + 1)
}
```

```{r}
# Specify m_q(x) = E[Y | X=x, Q=q], as defined in Section 4
# In the notation of the rest of the paper, m_2(x) = \mu(x)
# and m_1(x)-m_0(x) = Delta(x)
m_fun <- function(x, q, interact, beta) {
  len_check <- check_len_two(beta)
  x <- as.numeric(x)
  Delta <- Delta_fun(x)
  m0 <- 1 + x + 0.5*x^2
  m1 <- m0 + Delta
  m2 <- beta[1] + beta[2] * Delta + interact*x
  return((q==0)*m0 + (q==1)*m1 + (q==2)*m2)
}
```

```{r}
# Specify \bar{mu}(x)
mu_bar_fun <- function(x, beta_bar) {
  n <- length(x)
  Delta_mat <- cbind(rep(1, n), Delta_fun(x))
  return(Delta_mat %*% beta_bar)
}
```

```{r}
# Specify r(x) = P(Q=1 | X=x, Q!=2), from Kallus et al. (2018)
r_fun <- function(x) {
  x <- as.numeric(x)
  return(rep(0.5, length(x)))
}
```

```{r}
# Specify \pi(x) = P(Q=2 | X=x)
pi_fun <- function(x, n, N, mu0, mu1, var0, var1) {
  rho <- n / (n + N)
  x <- as.numeric(x)
  f_rct <- dnorm(x, mean=mu1, sd=sqrt(var1))
  f_obs <- dnorm(x, mean=mu0, sd=sqrt(var0))
  x_den <- f_rct * rho + f_obs * (1-rho)
  return((f_rct * rho) / x_den) # Bayes' rule
}
```

```{r}
## Densities of covariate distributions
x_rct_density <- function(x, mu1, var1) { 
  dnorm(x, mean=mu1, sd=sqrt(var1)) 
}
x_obs_density <- function(x, mu0, var0) {
  dnorm(x, mean=mu0, sd=sqrt(var0))
}
```

```{r}
# Compute true params for simulations
get_true_params <- function(beta, interact, mu0, mu1, var0, var1) {
  len_check <- check_len_two(beta)
  
  ## Instantiate covariate densities
  f_rct <- function(x) x_rct_density(x, mu1, var1)
  f_obs <- function(x) x_obs_density(x, mu0, var0)

  ## E_{obs}[\Delta(X)]
  Delta_mean_obs <- integrate(f=function(x) Delta_fun(x)*f_obs(x), lower=-Inf, upper=Inf)$value
  
  ## True ATE on target population
  tau <- beta[1] + beta[2] * Delta_mean_obs + interact * mu0
  
  ## E_{rct}[\Delta(X)^k], k=1,2
  Delta_mean_rct <- integrate(f=function(x) Delta_fun(x)*f_rct(x), lower=-Inf, upper=Inf)$value
  Delta_sq_mean_rct <- integrate(f=function(x) Delta_fun(x)^2*f_rct(x), lower=-Inf, upper=Inf)$value
  
  ## True ATE in RCT population
  mean_y_rct <- beta[1] + beta[2] * Delta_mean_rct + interact * mu1 
  
  ## E_{rct}[X\Delta(X)]
  interact_Delta_mean_rct <- integrate(f=function(x) Delta_fun(x)*x*f_rct(x), lower=-Inf, upper=Inf)$value
  
  ## E_{rct}[Y\Delta(X)] = E_{rct}[\mu(X)*\Delta(X)]
  mean_y_Delta_rct <- beta[1] * Delta_mean_rct + beta[2] * Delta_sq_mean_rct + interact * interact_Delta_mean_rct
  
  ## Compute beta_bar
  Mat <- matrix(c(1, Delta_mean_rct,
                  Delta_mean_rct, Delta_sq_mean_rct), nrow=2)
  beta_bar <- (solve(Mat) %*% c(mean_y_rct, mean_y_Delta_rct))
  
  ## Projected ATE
  tau_bar <- beta_bar[1] + beta_bar[2] * Delta_mean_obs 
  
  return(list(tau=tau, tau_bar=tau_bar, beta_bar=beta_bar))
}
```


```{r}
# return a function giving weights w(x) s.t. \bar{\tau} = E_{obs}[w(X)\mu(X)]
# the weights w(x) are chosen to have minimal variance among those considered
# in Proposition 1
get_w_fun <- function(beta, interact, mu0, mu1, var0, var1) {
  f_rct <- function(x) x_rct_density(x, mu1, var1)
  f_obs <- function(x) x_obs_density(x, mu0, var0)
  Lam <- function(x) f_rct(x) / f_obs(x)
  
  beta_bar <- get_true_params(beta, interact, mu0, mu1, var0, var1)$beta_bar
  mu_bar_fun <- function(x) beta_bar[1] + beta_bar[2] * Delta_fun(x)
  mu_fun <- function(x) beta[1] + beta[2] * Delta_fun(x) + interact * x
  
  # Set integration bounds +/- 10 SD for numerical stability
  lower1 <- mu1 - 10*sqrt(var1)
  upper1 <- mu1 + 10*sqrt(var1)
  lower0 <- mu0 - 10*sqrt(var0)
  upper0 <- mu0 + 10*sqrt(var0)
  A11 <- integrate(f=function(x) Lam(x)*f_rct(x)*(mu_fun(x)-mu_bar_fun(x))^2,
                   lower=lower1, upper=upper1)$value
  A12 <- integrate(f=function(x) Lam(x)*f_rct(x)*(mu_fun(x)-mu_bar_fun(x))^2*Delta_fun(x),
                   lower=lower1, upper=upper1)$value
  A22 <- integrate(f=function(x) Lam(x)*f_rct(x)*(mu_fun(x)-mu_bar_fun(x))^2*Delta_fun(x)^2,
                   lower=lower1, upper=upper1)$value
  b1 <- integrate(f=function(x) f_rct(x)*mu_fun(x)*(mu_fun(x)-mu_bar_fun(x)),
                  lower=lower1, upper=upper1)$value
  b2 <- integrate(f=function(x) f_rct(x)*mu_fun(x)*(mu_fun(x)-mu_bar_fun(x))*Delta_fun(x),
                  lower=lower1, upper=upper1)$value
  A <- matrix(c(A11, A12, A12, A22), nrow=2)
  b <- c(b1, b2)
  lam_den <- as.numeric(t(b) %*% solve(A) %*% b)
  lam <- -1 * integrate(f=function(x) f_obs(x)*(mu_fun(x)-mu_bar_fun(x)), lower=lower0, upper=upper0)$value / lam_den
  gamma <- -1 * lam * (solve(A) %*% b)
  w_fun <- function(x) 1 - Lam(x) * (mu_fun(x)-mu_bar_fun(x)) * (gamma[1] + gamma[2] * Delta_fun(x))
  return(w_fun)
}
```

```{r}
# Function to generate simulated data
gen_data <- function(n, N, mu0, mu1, var0, var1, interact, beta, seed=NULL) {

  ## Generate X
  set.seed(seed)
  X_rct <- rnorm(n, mean=mu1, sd=sqrt(var1))
  X_obs <- rnorm(N, mean=mu0, sd=sqrt(var0))

  ## Instantiate mean functions
  m0 <- function(x) m_fun(x, 0, interact=interact, beta=beta)
  m1 <- function(x) m_fun(x, 1, interact=interact, beta=beta)
  m2 <- function(x) m_fun(x, 2, interact=interact, beta=beta)

  ## Generate y, z
  y_rct <- m2(X_rct) + rnorm(n, sd=sqrt(1^2+0.5^2))
  z_obs <- rbinom(n=N, size=1, prob=r_fun(X_obs))
  y_obs <- z_obs * m1(X_obs) + (1-z_obs) * m0(X_obs) + rnorm(N, sd=sqrt(0.75^2+0.5^2))

  ## Put variables together into single data frame
  rct_df <- data.frame(X_rct) %>%
    mutate(y=y_rct, z=0)
  colnames(rct_df) <- c("x", "y", "z")
  obs_df <- data.frame(X_obs) %>%
    mutate(y=y_obs, z=z_obs)
  colnames(obs_df) <- c("x", "y", "z")
  return(list(rct_df=rct_df, obs_df=obs_df))
}
```

# Run 1d sims

Estimators:

- AIPSW: $\hat{\tau}_{\aipsw} = \frac{1}{n}\sum_{i=1}^n(Y_i-\hat{\mu}(X_i))\frac{n}{N}\hat{q}_{n,N}(X_i) + \frac{1}{N} \sum_{i=n+1}^{n+N} \hat{\mu}(X_i)$
- Outcome regression: $\hat{\tau}_{\or} = \frac{1}{N} \sum_{i=n+1}^{n+N} \hat{\bar{\mu}}(X_i)$
- collab: $\hat{\tau}_{\collab} = \frac{1}{n}\sum_{i=1}^n \frac{n}{N}\left[(Y_i-\hat{\mu}(X_i))\hat{g}_{n,N}(X_i) + \frac{\hat{q}_{n,N}(X_i)}{1+\hat{q}_{n,N}(X_i)}(\hat{\mu}(X_i)-\hat{k}(X_i))\right]+ \frac{1}{N} \sum_{i=n+1}^{n+N} \frac{\hat{q}_{n,N}(X_i)\hat{\mu}(X_i) + \hat{k}(X_i)}{1+\hat{q}_{n,N}(X_i)}$

Nuisance estimation procedures

1. `aipsw`, `or`, and `collab`: 
- Estimate $q_{n,N}$ using logistic GAM, where $q_{n,N}(x) = P(S=0 | X=x) / P(S=1 | X=x)$ is an odds ratio
- Estimate $\Delta$ via DR learner, with GAM's as base learners and $r$ learned via logistic GAM
- Estimate $\mu$ via simple linear regression of $y$ in RCT on $\hat{\Delta}(x)$ (this is really estimating $\bar{\mu}$)
- Estimate $g$, $k$ using logistic GAM (for `collab` only). Need to figure out why offset...
2. `aipsw_extrap`, `or_extrap`, and `collab_extrap`:
- Estimate $q_{n,N}$ using logistic GAM
- Estimate $\Delta$ via DR learner, with GAM's as base learners and $r$ learned via logistic GAM
- Estimate $\mu$ via superlearner to predict $y$ in RCT from $x$ and $\hat{\Delta}(x)$ (extrapolates!)
- Estimate $g$, $k$ using logistic GAM and estimated $\mu$, $q_{n,N}$ (for `collab` only). Need to figure out offset issue from semi-supervised paper...
3. `aipsw_oracle`, `or_oracle`: 
- Assume $q_{n,N}$, $\Delta$, $\mu$ all known
4. `or_Delta_oracle`
- Estimate $\bar{\mu}$ via simple linear regression of $y$ in RCT on true $\Delta(x)$
5. `or_bar_oracle`
- Uses true $\bar{\mu}$ (differs from `or_oracle` which uses true $\mu$)

Top line should be comparing estimation of $\tau$ by `aipsw_extrap` and `collab_extrap` vs. estimation of $\bar{\tau}$ with `or`.

We can also compare `or` vs. `or_Delta_oracle` to verify that estimation of $\Delta$ is asymptotically negligible.

```{r}
run_1d_sims <- function(n_sims, n, N, mu0, mu1, var0, var1, interact, beta, 
                        init_seed=NULL) {
  
  # Preallocate data frames for estimators and CI's
  aipsw <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                      ci_upper=rep(NA, n_sims))
  or <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                   ci_upper=rep(NA, n_sims))
  collab <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                        ci_upper=rep(NA, n_sims))
  aipsw_extrap <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                            ci_upper=rep(NA, n_sims))
  or_extrap <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                         ci_upper=rep(NA, n_sims))
  collab_extrap <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                               ci_upper=rep(NA, n_sims))
  aipsw_oracle <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                             ci_upper=rep(NA, n_sims))
  or_oracle <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                          ci_upper=rep(NA, n_sims))
  or_bar_oracle <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                              ci_upper=rep(NA, n_sims))
  or_Delta_oracle <- data.frame(theta_hat=rep(NA, n_sims), ci_lower=rep(NA, n_sims),
                              ci_upper=rep(NA, n_sims))
  beta_hats <- matrix(NA, nrow=n_sims, ncol=2)
  
  for (i in 1:n_sims) {
    ## Set seed
    if (is.null(init_seed)) {
      curr_seed <- NULL
    } else {
      curr_seed <- init_seed + i - 1
    }
    
    ## Generate simulated data
    data <- gen_data(n=n, N=N, mu0=mu0, mu1=mu1, var0=var0, var1=var1, 
                     interact=interact, beta=beta, seed=curr_seed)
    rct_df <- data$rct_df
    obs_df <- data$obs_df
    all_df <- rbind(rct_df, obs_df)
    all_df$s <- c(rep(1, n), rep(0, N))
      
    ## Compute nuisance estimates
    ## learn pi via logistic GAM
    pi_hat_model <- mgcv::gam(s ~ s(x), data=all_df, family=binomial(link="logit"))
    all_df$pi_hat <- predict(pi_hat_model, type="response")
    
    ## learn r
    x_rct <- rct_df$x
    x_obs <- obs_df$x
    x_obs_ctl <- as.matrix(x_obs[obs_df$z==0])
    r_hat_model <- mgcv::gam(z ~ s(x), data=all_df[all_df$s==0,], 
                       family=binomial(link="logit"))
    all_df$r_hat <- predict(r_hat_model, newdata=all_df, type="response")

    ## learn Delta via DR learner
    obs_df <- all_df[all_df$s==0,]
    a01 <- all_df[all_df$s==0 & all_df$z==1,]
    a00 <- all_df[all_df$s==0 & all_df$z==0,]
    m01_model <- mgcv::gam(y ~ s(x), data=a01)
    m00_model <- mgcv::gam(y ~ s(x), data=a00)
    obs_df$m01_hat <- predict(m01_model, newdata=obs_df)
    obs_df$m00_hat <- predict(m00_model, newdata=obs_df)
    obs_df$m_hat <- with(obs_df, z*m01_hat + (1-z)*m00_hat)
    obs_df$po <- with(obs_df, (z-r_hat)/(r_hat*(1-r_hat)) * (y-m_hat) + m01_hat-m00_hat)
    Delta_model <- mgcv::gam(po ~ s(x), data=obs_df)
    all_df$Delta_hat <- predict(Delta_model, newdata=all_df)

    ## estimate beta, and use to estimate m1
    naive_lm <- lm(y ~ Delta_hat, data=all_df, subset=all_df$s==1)
    beta_hat <- coef(naive_lm)
    all_df$mu_hat <- beta_hat[1] + beta_hat[2] * all_df$Delta_hat

    ## estimate g via logistic gam with offset
    all_df$offset <- qlogis(n / (n+N))
    g_hat_reg <- mgcv::gam(s ~ s(mu_hat) + offset(offset), family=binomial(link=logit),
                           data=all_df)
    all_df$g_hat <- predict(g_hat_reg, type="response")

    ## estimate k via GAM
    k_hat_reg <- mgcv::gam(mu_hat ~ s(pi_hat), data=all_df)
    all_df$k_hat <- predict(k_hat_reg, type="response")

    ## estimate m1 as a function of both x and Delta_hat(x), and extrapolate
    ## residualization approach
    ## this is what you would do if you believed there is some overlap
    m1_reg <- SuperLearner(Y=rct_df$y, X=all_df[all_df$s==1, c("x", "Delta_hat")], 
                           SL.library=c("SL.glmnet", "SL.earth", "SL.randomForest", "SL.svm"))
    all_df_extrap <- all_df
    all_df_extrap$mu_hat <- as.numeric(predict(m1_reg, newdata=all_df_extrap[,c("x", "Delta_hat")])$pred)
    
    ## estimate g_hat via logistic gam with offset
    all_df_extrap$offset <- qlogis(n / (n+N))
    g_hat_reg_extrap <- tryCatch (
      {
        mgcv::gam(s ~ s(mu_hat) + offset(offset), 
                  family=binomial(link=logit),
                  data=all_df_extrap)
      },
      error = function(e) {
        message("GAM failed, fitting ordinary logistic regression instead.")
        mgcv::gam(s ~ mu_hat + offset(offset), 
                  family=binomial(link=logit),
                  data=all_df_extrap)
      }
    )
    all_df_extrap$g_hat <- predict(g_hat_reg_extrap, type="response")

    ## estimate k_hat via GAM
    k_hat_reg_extrap <- tryCatch(
      {
        mgcv::gam(mu_hat ~ s(pi_hat), data=all_df_extrap)
      },
      error = function(e) {
        message("GAM failed, fitting ordinary linear regression instead.")
        mgcv::gam(mu_hat ~ pi_hat, data=all_df_extrap)
      }
    )
    all_df_extrap$k_hat <- predict(k_hat_reg_extrap, type="response")
    
    ## generate oracle data frame (knows all nuisance functions)
    all_df_oracle <- all_df[,c("s", "y", "x")]
    all_df_oracle$Delta_hat <- Delta_fun(all_df_oracle[,"x"])
    all_df_oracle$pi_hat <- pi_fun(all_df_oracle[,"x"], n=n, N=N, mu0=mu0, mu1=mu1, var0=var0, var1=var1)
    all_df_oracle$mu_hat <- m_fun(all_df_oracle[,"x"], q=2, interact=interact, beta=beta)
    
    ## generate oracle Delta data frame (knows Delta)
    naive_lm <- lm(y ~ Delta_hat, data=all_df_oracle, subset=all_df_oracle$s==1)
    beta_hat_Delta_oracle <- coef(naive_lm)
    all_df_oracle_Delta <- all_df_oracle
    all_df_oracle_Delta$mu_hat <- beta_hat_Delta_oracle[1] + beta_hat_Delta_oracle[2] * all_df_oracle_Delta$Delta_hat
    
    ## generate oracle data frame for outcome regression bar
    all_df_oracle_bar <- all_df_oracle
    oracle_params <- get_true_params(beta=beta, interact=interact,
                                     mu0=mu0, mu1=mu1, var0=var0, var1=var1)
    all_df_oracle_bar$mu_hat <- oracle_params$beta_bar[1] + oracle_params$beta_bar[2] * all_df_oracle_bar$Delta_hat
    
    # Compute final estimators
    aipsw[i,] <- compute_estimator_and_ci(all_df, type="aipsw")
    aipsw_extrap[i,] <- compute_estimator_and_ci(all_df_extrap, type="aipsw")
    aipsw_oracle[i,] <- compute_estimator_and_ci(all_df_oracle, type="aipsw")
    collab[i,] <- compute_estimator_and_ci(all_df, type="collab")
    collab_extrap[i,] <- compute_estimator_and_ci(all_df_extrap, type="collab")
    or[i,] <- compute_estimator_and_ci(all_df, type="or")
    or_extrap[i,] <- compute_estimator_and_ci(all_df_extrap, type="or")
    or_oracle[i,] <- compute_estimator_and_ci(all_df_oracle, type="or")
    or_bar_oracle[i,] <- compute_estimator_and_ci(all_df_oracle_bar, type="or") # knows true m1
    or_Delta_oracle[i,] <- compute_estimator_and_ci(all_df_oracle_Delta, type="or") # knows true Delta_0 and estimates tau_bar
    
    # Store beta_hat
    beta_hats[i,] <- beta_hat
  }
  sim_params <- list(n=n, N=N, mu0=mu0, mu1=mu1, var0=var0, var1=var1, 
                     interact=interact, beta=beta, init_seed=init_seed)
  return(list(aipsw=aipsw, collab=collab, or=or, 
              aipsw_extrap=aipsw_extrap, collab_extrap=collab_extrap, or_extrap=or_extrap,
              aipsw_oracle=aipsw_oracle, or_oracle=or_oracle, or_bar_oracle=or_bar_oracle,
              or_Delta_oracle=or_Delta_oracle, beta_hats=beta_hats, sim_params=sim_params))
}
```

```{r}
theta_list <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)
n_params <- length(theta_list)
```

```{r}
# # Run sims
# sim_results <- vector("list", length(theta_list))
# for (i in 1:n_params) {
#   theta <- theta_list[i]
#   cat("theta =", theta, "\n")
#   sim_params <- list(n_sims=1000, n=100, N=10000, mu0=0, mu1=-1*theta, var0=1, 
#                      var1=1-theta, interact=-1, beta=c(0, 1), init_seed=1)
#   sim_results[[i]] <- do.call(run_1d_sims, sim_params)
# }
```

```{r}
# # Save results
# saveRDS(sim_results, paste0(PATH, "sim_results_1d.rds"))
```

# Evaluate sim results

```{r}
evaluate_sim_results <- function(sim_res) {
  sim_params <- sim_res$sim_params
  rho <- with(sim_params, n/(n+N))
  
  params <- with(sim_params, get_true_params(beta, interact, mu0, mu1, var0, var1))
  
  # Compute summary stats
  sim_ests <- sim_res[1:(length(sim_res)-2)]
  mse <- sapply(sim_ests, function(est_df) mean((est_df$theta_hat-params$tau)^2))
  mse_bar <- sapply(sim_ests, function(est_df) mean((est_df$theta_hat-params$tau_bar)^2))
  bias <- sapply(sim_ests, function(est_df) mean(est_df$theta_hat) - params$tau)
  bias_bar <- sapply(sim_ests, function(est_df) mean(est_df$theta_hat) - params$tau_bar)
  vrnce <- sapply(sim_ests, function(est_df) var(est_df$theta_hat))
  cvg <- sapply(sim_ests, function(est_df) mean((est_df$ci_lower <= params$tau & est_df$ci_upper >= params$tau)))
  cvg_bar <- sapply(sim_ests, function(est_df) mean((est_df$ci_lower <= params$tau_bar & est_df$ci_upper >= params$tau_bar)))
  widths <- sapply(sim_ests, function(est_df) mean(est_df$ci_upper - est_df$ci_lower))
  
  # beta_bar
  n_sim <- nrow(sim_ests[[1]])
  beta_hat_bar_df <- data.frame(int_mean=mean(sim_res$beta_hats[,1]),
                                slope_mean=mean(sim_res$beta_hats[,2]),
                                int_se=sd(sim_res$beta_hats[,1])/sqrt(n_sim),
                                slope_se=sd(sim_res$beta_hats[,2])/sqrt(n_sim),
                                int_bar=params$beta_bar[1],
                                slope_bar=params$beta_bar[2])
  # Aggregate results into data frame
  res_df <- data.frame(mse=mse, mse_bar=mse_bar, bias=bias, bias_bar=bias_bar,
                       vrnce=vrnce, cvg=cvg, cvg_bar=cvg_bar, widths=widths)
  return(list(res_df=res_df, beta_hat_bar_df=beta_hat_bar_df, 
              beta_hats=sim_res$beta_hats, sim_params=sim_params,
              params=params))
}
```

## Plot results

```{r}
sim_results <- readRDS(paste0(PATH, "sim_results_1d.rds"))
```

```{r}
# Function to compute and plot weights
plot_wts <- function(eval_results, n) {
  
  ## Generate x
  z <- seq(-4, 4, length.out=n)
  
  ## Compute weights
  wt_dfs <- lapply(eval_results, function(res) {
    wt_fun <- with(res$sim_params, get_w_fun(beta, interact, mu0, mu1, var0, var1))
    x <- with(res$sim_params, sqrt(var0)*z + mu0)
    all_wts <- wt_fun(x)
    return(data.frame(x=x, w=all_wts, theta=-1*res$sim_params$mu1))
  })

  all_wt_df <- do.call(rbind, wt_dfs)
  
  ## Plot weights using faceting
  wt_plot <- all_wt_df %>%
    ggplot(aes(x=x, y=w)) +
    geom_line() +
    facet_wrap(~theta, labeller = labeller(theta = function(x) paste(expression(theta), "=", x))) +
    labs(x="x", y="weight") +
    scale_y_continuous(limits=c(0, 2),)
  return(wt_plot)
}
```


```{r}
## Function to convert eval results to a dataframe for plotting
convert_to_plot_df <- function(eval_results, colnames) {
  res_list <- lapply(eval_results, function(res) {
    raw_df <- as.data.frame(res$res_df[colnames])
    stopifnot(!any(grepl(";", colnames(raw_df))))
    colnames(raw_df) <- paste(colnames(raw_df), -1*res$sim_params$mu1, sep=";")
    return(raw_df)
  })
  plot_df <- do.call(cbind, res_list) %>%
    rownames_to_column(var="estimator") %>%
    pivot_longer(cols=-c("estimator"), names_to=c("metric", "theta"), 
                 names_sep=";", values_to="value")
  return(plot_df)
}
```

```{r}
# Process results
# options(scipen=999)
eval_results <- lapply(sim_results, evaluate_sim_results)
```

```{r}
# Generate plot df
plot_df <- convert_to_plot_df(eval_results,
                              colnames=c("mse", "mse_bar", "cvg", "cvg_bar", "bias", "bias_bar", "vrnce", "widths"))
```


```{r}
# MSE plot
plot_df %>%
  filter((metric %in% c("vrnce", "bias_bar") & estimator == "or") | (metric %in% c("vrnce", "bias") & estimator %in% c("aipsw_extrap", "collab_extrap"))) %>%
  mutate(metric=ifelse(metric=="vrnce", "vrnce", "bias_sq"),
         value=ifelse(metric=="bias_sq", value^2, value)) %>% # get sq. bias
  ggplot(aes(x=estimator, y=value, fill=estimator, alpha=metric)) +
  facet_wrap(~ theta, nrow=2, scales="free",
             labeller=label_bquote(col = theta == .(theta))) +
  geom_col(position="stack", color="black") +
  scale_alpha_manual(
    values = c("vrnce" = 1, "bias_sq" = 0),
    guide = "none" # Hide the fill legend if it's confusing
  ) +
  scale_fill_brewer(
    palette = "Set1",
    labels = c("aipsw_extrap" = expression(hat(tau)[aipsw]), 
               "collab_extrap" = expression(hat(tau)[collab]), 
               "or"  = expression(hat(bar(tau))))
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.text = element_text(size = 14, face = "bold")) + 
  labs(x="", y="")
ggsave(filename=paste(PATH, "mse_plot_1d_sim.png", sep=""))
```



```{r}
# CI table
plot_df %>%
  filter((metric %in% c("cvg_bar", "widths") & estimator=="or") | (metric %in% c("cvg", "widths") & estimator %in% c("aipsw_extrap", "collab_extrap"))) %>%
  pivot_wider(names_from=c(estimator, metric), values_from=value)
```

```{r}
# CI table
plot_df %>%
  filter((metric %in% c("cvg_bar", "width") & estimator=="or") | (metric == "cvg") & (estimator %in% c("aipsw_extrap", "collab_extrap"))) %>%
  select(-metric) %>%
  pivot_wider(names_from=estimator, values_from=value)
```

```{r}
# Compare oracle and non-oracle MSE
plot_df %>%
  filter((metric=="mse_bar" & estimator %in% c("or", "or_Delta_oracle")) |
         (metric=="mse" & estimator %in% c("aipsw", "aipsw_oracle"))) %>%
  select(-metric) %>%
  pivot_wider(names_from=estimator, values_from=value) %>%
  transmute(theta=theta, aipsw=aipsw/aipsw_oracle, or=or/or_Delta_oracle)
```

```{r}
# Weight plots
wt_fun_list <- lapply(eval_results, function(res) {
  params <- res$sim_params
  wts <- with(params, get_w_fun(beta=beta, interact=interact, mu0=mu0, mu1=mu1, 
                                var0=var0, var1=var1))
  return(wts)
})
x_wt <- seq(-4, 4, length.out=1000)
wts <- data.frame(sapply(wt_fun_list, function(wt_fun) wt_fun(x_wt)))
names(wts) <- theta_list
wts$x <- x_wt
wt_plot <- wts %>% 
  pivot_longer(cols=-x, names_to="theta", values_to="wt") %>%
  ggplot(aes(x=x, y=wt)) +
  geom_line(color="red") +
  geom_abline(slope=0, intercept=1, linetype="dotted", color="black") +
  facet_wrap(~ theta, nrow=2,
             labeller=label_bquote(col = theta == .(theta))) +
  theme_minimal() + 
  theme(strip.text = element_text(size = 14, face = "bold")) + 
  labs(x="x", y="") +
  scale_y_continuous(limits = c(0, 2))
ggsave(filename=paste(PATH, "wt_plot_1d_sim.png", sep=""))
```

```{r}

```


